AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-15 publications/iaai21/dora_outlier_detection_iaai.tex
Update PAE results and figure for planetary rover (#13,#60).
Add notes to Hannah in todos. (#42)

\subsubsection{Targets in Mars rover images.}
% We initialized each algorithm with $D_s$ and requested a ranking of
% targets in $D_{s+}$.
\todo{Consider merging all three data set discussions since they are
in one table? with their own figures? The point here isn't really to
compare algs or data sets but instead to show that we CAN compare
them, using DORA.}
%
Table~\ref{tab:faw_results} compares the performance of each ranking 
algorithm by reporting the precision obtained when the number of
selections is the same as the total number of outliers.  We could not
employ RX in this case since the data dimensionality ($64 \times 64 =
4096$) exceeded the data set size.  We found that
the Isolation Forest achieved the highest precision (best outlier
detection) when allowed to select only \num{9} images.
Figure~\ref{fig:planetary_results} shows the complete (cumulative)
outlier detection performance for each algorithm when ranking
all \num{58} target images in $D_{1694-1703}$. \todo{Explain MDR the first
time it appears. }

\subsubsection{Satellite time series for ground-truth observations.}
We used the full dataset of 6,757 samples to fit the ranking algorithms and
used the independently-labeled set of 113 points in Kenya for evaluation.
Table \ref{fig:faw_results} compares the performance of each ranking 
algorithm by plotting the number of true outliers detected out of the top
$N$ selections. We reported the area under the curve (AUC), normalized
by the total number of selections, in the legend
for each algorithm to give a quantitative comparison of the curves.
Table \ref{tab:faw_results} gives the precision at $N$ where
$N=n_{outlier}=37$. The negative sampling algorithm had the best performance
in both metrics. DEMUD, PCA, and PAE tied for the lowest precision at 
$N=n_{outlier}$ while DEMUD and PCA tied for the lowest
AUC. \todo{For completeness, Explain why no LRX here.}

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for three applications; the
  best result for each data set is in bold.}
  \label{tab:faw_results}
  \centering
  \begin{tabular}{l|ccc}
    \hline
    Algorithm & Astrophysics & Earth & Planetary \\
    \hline
    PCA               & & 0.41 & 0.44 \\
    DEMUD             & & 0.41 & 0.44 \\
    \hline
    RX                & & 0.43 & ---- \\
    LRX               & & ---- & 0.33 \\
    \hline
    Isolation Forest  & & 0.46 & \textbf{0.56} \\
    \hline
    PAE               & & 0.41 & 0.22 \\
    Neg. Sampling & & \textbf{0.49} & 0.33 \\
    \hline
    Random            & & 0.32 & 0.11 \\
    \hline
  \end{tabular}
\end{table}

>>>>

\subsubsection{Targets in Mars rover images.}
% We initialized each algorithm with $D_s$ and requested a ranking of
% targets in $D_{s+}$.
\todo{Hannah: Consider merging all three data set discussions since they are
in one table? with their own figures? The point here isn't really to
compare algs or data sets but instead to show that we CAN compare
them, using DORA.}
%
Table~\ref{tab:faw_results} compares the performance of each ranking 
algorithm by reporting the precision obtained when the number of
selections is the same as the total number of outliers.  We could not
employ RX in this case since the data dimensionality ($64 \times 64 =
4096$) exceeded the data set size.  We found that
the Isolation Forest achieved the highest precision (best outlier
detection) when allowed to select only \num{9} images.
Figure~\ref{fig:planetary_results} shows the complete (cumulative)
outlier detection performance for each algorithm when ranking
all \num{58} target images in $D_{1694-1703}$. \todo{Hannah: Explain
MDR the first time it appears. }

\subsubsection{Satellite time series for ground-truth observations.}
We used the full dataset of 6,757 samples to fit the ranking algorithms and
used the independently-labeled set of 113 points in Kenya for evaluation.
Table \ref{fig:faw_results} compares the performance of each ranking 
algorithm by plotting the number of true outliers detected out of the top
$N$ selections. We reported the area under the curve (AUC), normalized
by the total number of selections, in the legend
for each algorithm to give a quantitative comparison of the curves.
Table \ref{tab:faw_results} gives the precision at $N$ where
$N=n_{outlier}=37$. The negative sampling algorithm had the best performance
in both metrics. DEMUD, PCA, and PAE tied for the lowest precision at 
$N=n_{outlier}$ while DEMUD and PCA tied for the lowest
AUC. \todo{Hannah: Update AUC -> MDR and for completeness, explain why
no LRX here.}

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for three applications; the
  best result for each data set is in bold.}
  \label{tab:faw_results}
  \centering
  \begin{tabular}{l|ccc}
    \hline
    Algorithm & Astrophysics & Earth & Planetary \\
    \hline
    PCA               & & 0.41 & 0.44 \\
    DEMUD             & & 0.41 & 0.44 \\
    \hline
    RX                & & 0.43 & ---- \\
    LRX               & & ---- & 0.33 \\
    \hline
    Isolation Forest  & & 0.46 & \textbf{0.56} \\
    \hline
    PAE               & & 0.41 & 0.44 \\
    Neg. Sampling & & \textbf{0.49} & 0.33 \\
    \hline
    Random            & & 0.32 & 0.11 \\
    \hline
  \end{tabular}
\end{table}
